\documentclass[conference]{IEEEtran}
\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Anonymous)
   /Title  (Imagine-Then-Act Chunk Selection for Lightweight Vision-Language-Action Policies)
   /CreationDate (D:20260606140000)
   /Subject (Robotics)
   /Keywords (robot learning; vision-language-action; visual foresight; semantic reasoning)
}

\begin{document}

\title{Imagine-Then-Act Chunk Selection for Lightweight Vision-Language-Action Policies}

% Replace [add your ID here] after OpenReview assigns the SemRob submission ID.
\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

\maketitle

\begin{abstract}
% Author-written abstract only. RSS-style policy prohibits submitting text
% generated entirely by LLMs. Keep this concise: problem, method, evaluation,
% strongest quantitative result, and why SemRob should care.
TODO.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
% Target: 4-page workshop version. Suggested shape:
% 1 paragraph: lightweight VLA policies are now practical but brittle.
% 1 paragraph: stochastic action chunks create multiple possible futures.
% 1 paragraph: this work selects an action chunk before execution by judging
% imagined outcome images against the current subgoal.
% 1 short contribution list.

TODO.

\section{Related Work}
% Keep this tight for SemRob. Research-room related-work results should be
% sorted into these buckets:
% 1. visual MPC / visual foresight / video prediction
% 2. world models and imagination-based planning
% 3. best-of-N / CEM / candidate trajectory selection
% 4. VLM-as-critic / reward / verifier in robotics
% 5. VLA and lightweight VLA background
% 6. agentic LLM concepts only where directly relevant

\subsection{Visual Foresight and Imagination-Based Planning}
TODO cite visual MPC, visual foresight, action-conditioned video prediction,
and world-model planning. Connect them to this paper's first proof setting:
using simulator clone rollouts and renders as oracle imagined outcomes before
training a deployable action-conditioned visual dynamics model.

\subsection{Candidate Trajectory Selection}
TODO cite best-of-N sampling, CEM, model-predictive control, and trajectory
ranking methods. Frame this paper as chunk-level candidate selection for a
fixed lightweight VLA, not as post-hoc recovery after a failed rollout.

\subsection{VLM Critics and Robotic Verification}
TODO cite VLM-as-reward, VLM-as-critic, and semantic verifier work in robotics.
State the boundary clearly: the VLM judge scores predicted outcome images for
pre-execution selection only; final task success remains the environment
benchmark signal.

\subsection{Efficient Vision-Language-Action Policies}
TODO cite SmolVLA~\cite{shukor2025smolvla}, TinyVLA~\cite{wen2024tinyvla},
OpenVLA~\cite{kim2024openvla}, and broader robot foundation policies such as
RT-1~\cite{brohan2022rt1} and RT-2~\cite{zitkovich2023rt2}.

\subsection{Agentic Planning and Feedback}
TODO cite SayCan~\cite{ahn2022saycan}, Inner Monologue~\cite{huang2022inner},
Code as Policies~\cite{liang2022code}, ReAct~\cite{yao2022react}, and
Reflexion~\cite{shinn2023reflexion}. Tie this to SemRob topics: semantic
goal interpretation and policy steering. Keep this subsection short: the paper
is not mainly an LLM-agent paper.

\section{Method}
% Core claim: no base policy weight changes. The wrapper samples candidate
% action chunks, imagines their outcomes, judges the predicted images against
% the current subgoal, and executes only the selected chunk.

\subsection{Base Policy and Evaluation Harness}
TODO describe the fixed SmolVLA policy, observation/action interface, LIBERO
or ManiSkill environment, seeds, action budgets, and logging artifacts.

\subsection{Candidate Chunk Generation}
TODO define stochastic chunk sampling from the fixed lightweight VLA. Specify
candidate count, sampling parameters, action horizon, and whether candidates
share the same current observation and subgoal.

\subsection{Imagined Outcome Rendering}
TODO define the first proof path: clone simulator state, roll out each
candidate chunk without committing it to the real evaluation environment, and
render the resulting outcome image. Explain that this is an oracle-imagination
upper-bound diagnostic. Later work can replace this with a learned
action-conditioned visual dynamics or video prediction model.

\subsection{VLM-Guided Chunk Selection}
TODO define the visual judge inputs: current observation, predicted outcome
image, candidate metadata, and current subgoal. The judge ranks candidates
before execution. Only the selected chunk is committed to the benchmark
environment.

\subsection{Success Semantics}
TODO state explicitly: final task success is the environment benchmark success
signal, e.g., \texttt{info["success"]} or \texttt{is\_success}. The VLM judge
is a pre-execution candidate selector, not a final success detector.

\section{Experiments}
% Keep this evidence-first. Use matched seeds, same base policy, same action
% budget where possible. Do not overclaim from small probes.

\subsection{Setup}
TODO list suites, task IDs, episodes per task, compute environment, simulator
versions, policy checkpoint, and action-step protocol.

\subsection{Policy-Only Baseline}
TODO summarize the current routed SmolVLA baseline and cite the local artifact
paths in the camera-ready or supplement, not in the blinded submission.

\begin{table}[t]
\centering
\caption{Policy-only baseline reproduction on LIBERO. Fill with final
paper-scale numbers only.}
\label{tab:baseline}
\begin{tabular}{lrrrrr}
\toprule
Condition & Goal & Object & Spatial & Long & Avg \\
\midrule
Policy-only & TODO & TODO & TODO & TODO & TODO \\
Reference & TODO & TODO & TODO & TODO & TODO \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Imagine-Then-Act Selection Results}
TODO compare \texttt{policy\_only}, random candidate selection, oracle imagined
candidate selection, and VLM-guided imagined candidate selection. Report
success, action steps, wall-clock latency, candidate count, and judge accuracy
against environment outcomes where available.

\begin{table}[t]
\centering
\caption{Imagined chunk selection ablation. Keep all conditions matched by
seeds, base policy, and committed action budget unless explicitly stated.}
\label{tab:selection}
\begin{tabular}{lrrrr}
\toprule
Condition & Episodes & Success & $N$ & Latency \\
\midrule
Policy-only & TODO & TODO & 1 & TODO \\
Random chunk & TODO & TODO & TODO & TODO \\
Oracle imagined selector & TODO & TODO & TODO & TODO \\
VLM imagined selector & TODO & TODO & TODO & TODO \\
\bottomrule
\end{tabular}
\end{table}

\section{Discussion}
TODO explain when imagined chunk selection helps, when it fails, and whether
semantic visual judging is actually better than random or oracle-state
heuristic selection.

\section{Limitations}
% RSS requires a limitations section for main papers; SemRob follows RSS paper
% policy, so include it here too.
TODO include limited task coverage, simulator-only evidence, privileged
simulator-clone imagination, VLM judge brittleness, latency from evaluating
multiple candidates, no weight updates, and no real robot claim unless real
evidence is added.

\section{Conclusion}
TODO one paragraph: what was tested, strongest measured result, and why
pre-execution imagined chunk selection is a useful control layer for
lightweight VLA policies.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
